---
title: "hw1"
author: "Victoria DelaCruz"
date: "2023-10-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Assignment Title: Introduction to Basic Data Analysis in R

Introduction:

Data analysis is a fundamental skill for any data scientist or analyst. R is a powerful programming language for statistical analysis and data visualization. In this assignment, we'll learn how to calculate the mean and median of a dataset in R.

Example:

Let's start with a sample dataset:

R
Copy code
# Sample dataset
data <- c(12, 25, 18, 32, 40, 15, 21, 27, 36, 29)
We want to calculate the mean and median of this dataset. Here's how you can do it in R:
```{r}
data <- c(12, 25, 18, 32, 40, 15, 21, 27, 36, 29)
```

R
Copy code
# Calculate the mean
mean_result <- mean(data)
```{r}
mean_result <- mean(data)
```

# Calculate the median
median_result <- median(data)
```{r}
median_result <- median(data)
```

Now, it's your turn to practice. We have provided a dataset for you, and your task is to write the code to calculate the mean and median.

Your Task:

Create a new R script or RMarkdown document.

Use the following dataset:

R
Copy code
# Dataset for your assignment
assignment_data <- c(14, 27, 32, 19, 25, 21, 30, 35, 42, 24)
Calculate the mean of the assignment_data dataset and store it in a variable.

Calculate the median of the assignment_data dataset and store it in a variable.

Finally, print the mean and median results to the console.

Your completed R script or RMarkdown document should include comments to explain each step of your code.

Hints:

Remember to use the mean() and median() functions in R to calculate the mean and median, respectively.

You can print the results using the print() or cat() functions.

Good luck with your assignment!




